### 2019-07-05 manuscript.tex
Some more comments on Intro and Methods

This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices.  Our main interest in this study is to analyze how norms associate with behavioural intention.  We focus on whether women will likely genitally cut their daughters based on their current intention and that provides a relatively more detailed result on how FGC norms interacts FGC practice than using than what had already happened (e.g. women’s own FGC status).  The main norm theory tested in this paper was that women’s intention on practicing FGC on their daughters was dependent on other women’s intention on cutting their daughters within their community.  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in order to understand if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “daugher_ persistence” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.

@@

We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS).  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication \cf{checked in 1/09/19}.

Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daugher_ persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7253 respectively.  \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

Our main response variables were woman's behavioural intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.  The predictors selected based on literature (e.g., aforementioned above) were woman's FGC status and beliefs of FGC benefits (see supp for a list of questionnaire of FGC benefits).  The beliefs of FGC benefits were quantified using average score \cf{pls confirm} to identify the strength of benefits associating with fgc practice. We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}. Other socio demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs. rural) in addition to country.  Media use and gender awareness were scored.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

>>>>

\jdcmt{Think about a good \P\ structure here (and topic ss).}
This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices.  Our main interest in this study is to analyze how norms associate with behavioural intention.  We focus on whether women will likely genitally cut their daughters based on their current intention and that provides a relatively more detailed result on how FGC norms interacts FGC practice than using than what had already happened (e.g. women’s own FGC status).  The main norm theory tested in this paper was that women’s intention on practicing FGC on their daughters was dependent on other women’s intention on cutting their daughters within their community.  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in order to understand if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “daughter persistence” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.

\jdcmt{Do we really call our three models: daughter; persistence; and daughter persistence? It does not seem conducive to reader understanding.}

@@

\jd{What is added by ``and samples'' here?}

We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS).  We selected countries with: high FGC prevalence \cite{UNIC16}, and FGC benefit and gender awareness modules available from DHS. We found four countries, and used the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset \jdcmt{What data set did we not analyze? Can we just say we analyzed the newest available (see edits above)? Also: these are pretty old.} due to the lack of FGC benefits modules before this study finished for publication \cf{checked in 1/09/19}.

\jdcmt{Never use underscores without the url command; it messes up formatting.}
Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daughter persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7253 respectively.  \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

Our main response variables were woman's \jdcmt{I don't think this work adds anything; behavioural} reported intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.  \jdcmt{You are describing just some predictors; The predictors selected} \jdcmt{I don't know what is being conveyed here, can we lose it? based on literature (e.g., aforementioned above)} were woman's FGC status and beliefs about FGC benefits (see supp for the benefit questionnaire).  The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of benefits associating with fgc practice. We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}. Other socio-demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs. rural) in addition to country.  Media use and gender awareness were scored.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).
